### 2014-11-12 intro.tex

To the best of our knowledge, this is the first time that a declarative language
allows control over execution while staying declarative and without resorting to
meta-language constructs. This is crucial to our goal of being able to prove
programs correct since proofs can be constructed even in the presence of
coordination facts.  After briefly discussing related work, we present an
overview of the base language, with an example. In
Section~\ref{sec:coordination}, we introduce the current set of coordination
facts, followed by a description of the changes required to implement the
desired coordination mechanisms. In Section~\ref{sec:applications} we present
several applications and show coordination can improve programs without
destroying clarity or provability.

>>>>

To the best of our knowledge, this is the first time that a declarative language
allows control over execution while staying declarative and without resorting to
meta-language constructs. This is crucial to our goal of being able to prove
programs correct since proofs can be constructed even in the presence of
coordination facts.  After briefly discussing related work, we present an
overview of the base language, with an example. In
\sectref{sec:coordination}, we introduce the current set of coordination
facts, followed by a description of the changes required to implement the
desired coordination mechanisms. In \sectref{sec:applications} we present
several applications and show coordination can improve programs without
destroying clarity or provability.
